Predicting Levels of Sales for Newly Published Books \\ using Cost-Sensitive Ensemble Methods

### 2016-12-04 paper.tex
fixing the format style (to show the abstract)
adding text to the INTRODUCTION

\documentclass[a4paper,10pt,onecolumn,preprint,3p]{elsarticle}

@@

\journal{Journal of XXX}

@@

%\begin{frontmatter}

@@

\maketitle

@@

%\end{frontmatter}

@@

>>>>

\documentclass[a4paper,10pt,twocolumn,preprint,3p]{elsarticle}

@@

\journal{Journal of XXXXXXXXX}

@@

\begin{frontmatter}

@@

%\maketitle

@@

\end{frontmatter}

@@

Determining the number of copies of a new book should the publisher print, the 
so called {\em print run}, for delivery to bookstores is a challenging problem.
Thus, it is extremely important to develop an accurate predictive method which 
could forecast the future sales a new book will achieve, in order to optimise 
production schedules, improve the publishing company profits and minimise 
losses \cite{Zhao2001}.

Printing an adequate number of copies, but not too many, might reduce the number 
of unsold volumes, which could lead to losses. 
In another hand, if the number of printed copies is not enough, the publisher 
company might have temporary losses due to a lack of supply.

Moreover, according to results reported in \cite{Fildes2010,Saeed2008}, reducing 
the error in estimated sales leads to the improvement of sales predictions and 
thus, in an enhancement in the whole production process.

\textbf{UNDER CONSTRUCTION ;) }

To make the print run as close as possible to the actual level of sales, it is 
essential to have an estimation of those sales.
In this sense, this paper continues our previous work on book sales prediction 
\cite{Castillo2016books} in which the main factors influencing sales where 
analyzed in order to create a tool that the publisher can use to decide how many 
books should be printed.

In this paper, the challenge we are taking is determining the actual level of 
sales a new book will achieve.

The rest of this paper is structured as follows: 
A detailled review of the approaches related to sales prediction in similar scopes is presented in Section \ref{sec:soa}.
Then, Section \ref{sec:methodology} details the methodology considered in the present study. 
Obtained results after extensive experimentation are presented in Section \ref{sec:experiments_results}.
Finally, conclusions and future lines of work are presented in Section \ref{sec:conclusions_future_work}.

%*******************************************************************************
%										STATE OF THE ART
%*******************************************************************************
\section{State of the art on sales forecasting} 
\label{sec:soa}

\textbf{UNDER CONSTRUCTION ;) }
